%------------------------
% Example "Before" Resume — typical colorful template resume with common mistakes
% This is a fictional resume to demonstrate the contrast with CalibrCV output
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{tikz}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{geometry}
\usepackage{fontawesome5}
\usepackage{parskip}

\geometry{left=0in, right=0in, top=0in, bottom=0in}
\pagecolor{white}
\pagestyle{empty}

% Colors
\definecolor{sidebar}{HTML}{2C3E50}
\definecolor{accent}{HTML}{1ABC9C}
\definecolor{lightgray}{HTML}{EEEEEE}
\definecolor{darktext}{HTML}{333333}
\definecolor{medtext}{HTML}{666666}

\begin{document}

\noindent
\begin{tikzpicture}[remember picture, overlay]
  % Sidebar background
  \fill[sidebar] (current page.north west) rectangle ([xshift=6.5cm]current page.south west);
\end{tikzpicture}

\noindent
\begin{minipage}[t]{6.0cm}
\vspace{0.6cm}
\centering

% Profile photo placeholder
\begin{tikzpicture}
  \fill[accent] (0,0) circle (1.8cm);
  \fill[sidebar] (0,0) circle (1.65cm);
  \node[white] at (0,0) {\fontsize{28}{28}\selectfont\faUser};
\end{tikzpicture}

\vspace{0.4cm}
{\color{white}\fontsize{18}{22}\selectfont\bfseries Alex Chen}

\vspace{0.1cm}
{\color{accent}\fontsize{10}{12}\selectfont Software Developer}

\vspace{0.6cm}

% Contact info
{\color{accent}\fontsize{11}{13}\selectfont\bfseries CONTACT}\\[4pt]
{\color{white}\small
\faPhone\ \ (555) 123-4567\\[3pt]
\faEnvelope\ \ alex.chen@email.com\\[3pt]
\faMapMarker*\ \ San Francisco, CA
}

\vspace{0.6cm}

% Skills with bars
{\color{accent}\fontsize{11}{13}\selectfont\bfseries SKILLS}\\[6pt]
{\color{white}\small Python}\\[2pt]
\begin{tikzpicture}
  \fill[sidebar!70!black] (0,0) rectangle (4.5,0.2);
  \fill[accent] (0,0) rectangle (4.0,0.2);
\end{tikzpicture}\\[4pt]
{\color{white}\small JavaScript}\\[2pt]
\begin{tikzpicture}
  \fill[sidebar!70!black] (0,0) rectangle (4.5,0.2);
  \fill[accent] (0,0) rectangle (3.8,0.2);
\end{tikzpicture}\\[4pt]
{\color{white}\small React}\\[2pt]
\begin{tikzpicture}
  \fill[sidebar!70!black] (0,0) rectangle (4.5,0.2);
  \fill[accent] (0,0) rectangle (3.5,0.2);
\end{tikzpicture}\\[4pt]
{\color{white}\small Node.js}\\[2pt]
\begin{tikzpicture}
  \fill[sidebar!70!black] (0,0) rectangle (4.5,0.2);
  \fill[accent] (0,0) rectangle (3.3,0.2);
\end{tikzpicture}\\[4pt]
{\color{white}\small SQL}\\[2pt]
\begin{tikzpicture}
  \fill[sidebar!70!black] (0,0) rectangle (4.5,0.2);
  \fill[accent] (0,0) rectangle (3.0,0.2);
\end{tikzpicture}\\[4pt]
{\color{white}\small AWS}\\[2pt]
\begin{tikzpicture}
  \fill[sidebar!70!black] (0,0) rectangle (4.5,0.2);
  \fill[accent] (0,0) rectangle (2.5,0.2);
\end{tikzpicture}\\[4pt]
{\color{white}\small Docker}\\[2pt]
\begin{tikzpicture}
  \fill[sidebar!70!black] (0,0) rectangle (4.5,0.2);
  \fill[accent] (0,0) rectangle (2.2,0.2);
\end{tikzpicture}

\vspace{0.6cm}

% Languages
{\color{accent}\fontsize{11}{13}\selectfont\bfseries LANGUAGES}\\[4pt]
{\color{white}\small
English (Native)\\[2pt]
Mandarin (Conversational)
}

\vspace{0.6cm}

% Hobbies
{\color{accent}\fontsize{11}{13}\selectfont\bfseries HOBBIES}\\[4pt]
{\color{white}\small
Hiking, Photography,\\[2pt]
Gaming, Cooking,\\[2pt]
Reading tech blogs
}

\vspace{0.5cm}
\end{minipage}%
\hspace{0.3cm}%
\begin{minipage}[t]{12.7cm}
\vspace{0.6cm}

% About Me
{\color{accent}\fontsize{13}{15}\selectfont\bfseries ABOUT ME}\\[2pt]
{\color{accent}\rule{2cm}{1.5pt}}\\[6pt]
{\color{darktext}\small
I am a passionate software engineer with experience in web development and a love for building things. I enjoy working with teams and I'm always looking for new opportunities to grow my skills. My goal is to work at a company where I can make an impact and learn new technologies. I believe that with hard work and dedication, anything is possible.
}

\vspace{0.5cm}

% Work Experience
{\color{accent}\fontsize{13}{15}\selectfont\bfseries WORK EXPERIENCE}\\[2pt]
{\color{accent}\rule{2cm}{1.5pt}}\\[6pt]

{\color{darktext}\bfseries Software Developer} \hfill {\color{medtext}\small June 2023 -- Present}\\
{\color{medtext}\small TechCorp Inc. | San Francisco, CA}\\[4pt]
\begin{itemize}[leftmargin=12pt, itemsep=1pt, parsep=0pt, topsep=0pt]
  {\color{darktext}\small
  \item Worked on the backend team to develop new features for the main product
  \item Was responsible for writing code and fixing bugs in the codebase on a daily basis
  \item Helped with code reviews and collaborated with other developers on the team
  \item I used Python and JavaScript in my daily work and also used AWS for deployments
  \item Participated in agile ceremonies including standups and sprint planning meetings
  }
\end{itemize}

\vspace{0.3cm}

{\color{darktext}\bfseries Junior Developer Intern} \hfill {\color{medtext}\small Jan 2023 -- May 2023}\\
{\color{medtext}\small StartupXYZ | Austin, TX}\\[4pt]
\begin{itemize}[leftmargin=12pt, itemsep=1pt, parsep=0pt, topsep=0pt]
  {\color{darktext}\small
  \item Worked on various tasks assigned to me by the senior developers
  \item Learned React and Node.js while building features for the web application
  \item Fixed some bugs and improved the user interface of the dashboard
  }
\end{itemize}

\vspace{0.5cm}

% Projects
{\color{accent}\fontsize{13}{15}\selectfont\bfseries PROJECTS}\\[2pt]
{\color{accent}\rule{2cm}{1.5pt}}\\[6pt]

{\color{darktext}\bfseries E-commerce Website}\\[3pt]
{\color{darktext}\small
Built a full-stack e-commerce website using React, Node.js, and MongoDB. The website has user authentication, product listings, shopping cart, and payment processing with Stripe. I also added search functionality and deployed it on AWS.
}

\vspace{0.3cm}

{\color{darktext}\bfseries Weather App}\\[3pt]
{\color{darktext}\small
Created a weather application that shows current weather and forecasts. Used React for the frontend and integrated with the OpenWeatherMap API. The app is responsive and works on mobile devices.
}

\vspace{0.5cm}

% Education
{\color{accent}\fontsize{13}{15}\selectfont\bfseries EDUCATION}\\[2pt]
{\color{accent}\rule{2cm}{1.5pt}}\\[6pt]

{\color{darktext}\bfseries University of California, Berkeley} \hfill {\color{medtext}\small Aug 2019 -- May 2023}\\
{\color{medtext}\small B.S. in Computer Science}\\[2pt]
{\color{darktext}\small Relevant coursework: Data Structures, Algorithms, Databases, Operating Systems}

\vspace{0.5cm}

% References
{\color{medtext}\small\textit{References available upon request.}}

\end{minipage}

\end{document}
